Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-05-01 papers/ms.tex
update ms

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{---}
\revised{---}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Trio of Mini-Neptunes in Cep-Her}

@@

% 208 words (250 max)
\begin{abstract}
  %The best way to measure a planet's age is to ignore the planet and
  %pay attention to the star.
  Stellar positions and velocities from Gaia are yielding a new view
  of open cluster dispersal.  
  Here we present an analysis of a group
  of stars spanning Cepheus ($l=100^\circ$) to Hercules ($l=40^\circ$),
  hereafter the Cep-Her complex.  The group includes four Kepler
  Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in part of the Cep-Her complex
  called the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}.  Here
  we focus on the former three systems, which are in other regions of
  the association.  Based on kinematic evidence from Gaia, stellar
  rotation periods from TESS, and spectroscopy, these three objects
  are also $\approx$40 million years (Myr) old.  More specifically, we
  find that Kepler-1643 is $46^{+9}_{-7}$\,Myr old, based on its
  membership in a dense sub-cluster of the complex called RSG-5.
  KOI-7368 and KOI-7913 are $36^{+10}_{-8}$\,Myr old, and are in a
  diffuse region that we call CH-2.  Based on the transit shapes and
  high resolution imaging, all three objects are most likely planets,
  with false positive probabilities of $6\times10^{-9}$,
  $4\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively.  These planets demonstrate
  that mini-Neptunes with sizes of $\sim$2 Earth radii exist at ages
  of 40 million years.
\end{abstract}

@@

A few salient properties of the Kepler objects in Cep-Her can be
gleaned from Figure~\ref{fig:age}.  The stars span spectral types of
G8V (Kepler-1627) to K6V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$K8V.  And since a star with
Solar mass and metallicity arrives at the zero-age main sequence at
$t\approx40$ Myr \citep{choi_mesa_2016}, these stars are all in the
late stages of their pre-main-sequence contraction.

@@

To verify these parameters and to analyze youth
proxies such as the Li 6708\,\AA\ doublet and H$\alpha$, we acquired
spectra.  We also acquired high resolution imaging for each system, to
constrain the existence of visual companions, including possible bound
binaries.  The system-by-system details follow, and the relevant
results are also summarized in Table~\ref{tab:sysparams}.

\subsection{Kepler\,1643}

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<$$1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$
respectively \citep{chubak_2012}.  To infer the equivalent width of
the \ion{Li}{1} 6708\,\AA\ doublet, we followed the procedure
described by \citet{bouma_2021_ngc2516}.  This yielded a strong
detection: ${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with values
consistent at $<$$1$-$\sigma$ between the two epochs.   The quoted
value does not correct for the \ion{Fe}{1} blend at 6707.44\,\AA.  Given the purported age and
effective temperature of the star, the lithium equivalent width is
somewhat low.  We discuss this in greater depth in
Appendix~\ref{app:spectra}.

@@

\subsection{KOI-7913}

@@

\paragraph{Spectra}
We acquired Keck/HIRES spectra for KOI-7913 A on the night of 2021 Nov
13, and KOI-7913 B on the night of 2021 Oct 26.  The
\texttt{SpecMatch-Emp} machinery yielded $T_{\rm eff,A} = 4324 \pm
70\,{\rm K}$, and $T_{\rm eff,B} = 4038 \pm 70\,{\rm K}$.  The
remaining parameters were in agreement with those from the cluster
isochrone.  For the primary, we also found $[{\rm Fe/H}]= -0.06 \pm
0.09$, $v\sin i = 13.3 \pm 1.0\,\mkms$, and ${\rm RV}_{\rm sys} =
-17.8 \pm 1.1\,\mkms$.  For the secondary, these same parameters were
$[{\rm Fe/H}]= -0.01 \pm 0.09$, $v\sin i = 10.7 \pm 1.0\,\mkms$, and
${\rm RV}_{\rm sys} = -18.8 \pm 1.1\,\mkms$.  Neither of the KOI-7913
components shows strong lithium absorption, but this is expected given
their $\approx$K6V and $\approx$K8V spectral types.  They do however
both show H$\alpha$ in emission.  Broadly speaking, both observations
are consistent with a $\approx$40 Myr age for KOI-7913 (see
Appendix~\ref{app:spectra}).

@@

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.9\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ages more precise than a
    factor of three are emphasized. The Cep-Her planets are
    Kepler-1643~b ($\square$), KOI-7368~b ($\triangledown$),
    KOI-7913~Ab (X), and Kepler-1627~Ab (+).  Interesting trends in
    the population of planets younger than $10^8$ years old include {\it i)} their
    large sizes and {\it ii)} the lack of hot Jupiters.  The new
    objects of interest in Cep-Her have normal mini-Neptune sizes
    between 2 and 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

The most significant novelty about the planets in Kepler-1643,
KOI-7368, and KOI-7913 is that their sizes are normal relative to the
known population of mini-Neptunes from Kepler.  At field star ages,
mini-Neptune sizes span 1.8\,$R_\oplus$ to 3.6\,$R_\oplus$, with the
most common size being $\approx 2.4\,R_\oplus$
\citep[][Figure~7]{Fulton_et_al_2017}.  The known planets younger than
$10^8$ years are almost all larger, with sizes between 4 and
10$\,R_\oplus$
\citep{Mann_K2_33b_2016,David_et_al_2016,benatti_possibly_2019,david_four_2019,newton_tess_2019,rizzuto_tess_2020,bouma_cluster_2020,mann_toi1227_2022}.
Figure~\ref{fig:rp_period_age} explores this in more detail by showing
the sizes, orbital periods, and ages of the known transiting planets,
emphasizing planets with precise ages.  The smallest previously known
planets comparable to the new Cep-Her mini-Neptunes are AU~Mic~c
($3.0\pm0.2\,R_\oplus$, see \citealt{martioli_aumicbc_2021} and
\citealt{gilbert_flares_2022}), Kepler-1627~Ab ($3.8\pm0.2\,R_\oplus$;
\citealt{bouma_kep1627_2022}), and AU~Mic~d ($4.2\pm0.2\,R_\oplus$;
\citealt{plavchan_planet_2020}).

@@

RSG-5, and Kepler-1643's membership inside it, meet typical
expectations for a star claimed to be in an open cluster.  RSG-5 is an
obvious overdensity relative to the local field, and our membership
selection easily produces a clean pre-main-sequence locus in color
versus absolute magnitude (Figure~\ref{fig:age}).  CH-2, and KOI-7913
and KOI-7368's membership inside it, do not meet these expectations in
as obvious a manner.  This is because the CH-2 association is diffuse.

@@

Given its low density, in CH-2 a real star cluster?  For this
discussion, we adopt the definition that a star cluster is a group of
at least 12 stars that was physically associated at its time of
formation.  The ``12'' is set to distinguish star clusters from
high-order multiples \citep[see][]{krumholz_star_2019}.  We explicitly
do not require a ``star cluster'' to be gravitationally bound:
dissolved clusters as well as their tidal tails are included in our
adopted definition of ``clusters''.  We similarly do not require a
threshold number of stars per unit spatial volume.  The latter point
acknowledges that an important factor in cluster identification is
also density in velocity space.  Perhaps once stellar rotation periods
and chemical abundances reach the same level of ubiquity as stellar
proper motions, they might enable further refinement of our ability to
discover stars that formed as part of the same event.

@@

It would be a worthy exercise for future work to perform a similar
search for coeval phase-space neighbors on the entire dataset of known
exoplanet hosts.  For the time being, we can offer the anecdotal point
that in our experience, most stars do not have dozens of 40\,Myr
neighbors within a local volume of a few \!\kms\ and tens of parsecs.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her that were
observed by Kepler: RSG-5, CH-2, and the $\delta$~Lyr cluster.  In
\citet{bouma_kep1627_2022} as well as this work, we have shown that
these groups share similar ages, and have kinematic correlations that
suggest a common origin.  With that said, the membership and
kinematics of the other Cep-Her groups shown in
Figure~\ref{fig:XYZvtang} deserve independent attention.  An important
aspect of the remaining work will be to acquire radial velocities of a
large subset of the stars, to assess whether the traceback approach
could be applicable.  Wide-field spectroscopic surveys such as LAMOST
\citep{zhao_2012_LAMOST} or SDSS-V \citep{kollmeier_2017} could enable
such analyses, while also providing sensitivity to the Li 6708\,\AA\
line.  If Gaia DR3 provides RVS spectra for the brighter F and G
dwarfs, these would also contain the calcium infrared triplet as
another age indicator.  These indicators, combined with better
kinematics, would help in definitively unraveling the formation
history of the complex.

@@

Each system has multiple indicators of youth that support the reported
ages.  For Kepler-1643, the strongest youth indicator is its physical
and kinematic association with RSG-5.  Based on the color--absolute
magnitude diagram, we are able to select members of this cluster with
a false positive rate of a few percent (Figure~\ref{fig:age}).
Kepler-1643 is one such member.  While the stellar rotation period
period agrees with this assessment, the star's lithium equivalent
width is marginally low, which might motivate future exploration of
lithium depletion across FGKM stars in RSG-5 (see
Appendix~\ref{app:spectra}).

@@

%\clearpage
\acknowledgements
\raggedbottom
% Cycle 3 and 4
L.G.B{.} is supported by the Heising-Simons Foundation 51
Pegasi~b Fellowship and the NASA TESS GI Program (80NSSC21K0335
and 80NSSC22K0298).
R.K{.} is supported by the Heising-Simons Foundation.
J.L.C{.} is supported by NSF AST-2009840 and the NASA TESS GI Program
(80NSSC22K0299).
D.H. is supported by the Alfred P. Sloan Foundation and NASA (80NSSC19K0597).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%%
%We thank the TESS architects
%%(G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, J.~Jenkins)
%and the many TESS team members for their
%efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
%Finally, this research has made use of the Keck Observatory Archive (KOA),
%which is operated by the W. M. Keck Observatory and the NASA Exoplanet
%Science Institute (NExScI), under contract with the National
%Aeronautics and Space Administration.
%We also thank the Keck Observatory staff for their support of
%HIRES and remote observing.  We recognize the importance that the
%summit of Maunakea has within the indigenous Hawaiian community, and
%are deeply grateful to have the opportunity to conduct observations
%from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@

\section{Spectroscopic Youth Indicators}
\label{app:spectra}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
			\includegraphics[width=0.99\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.3cm}
	\caption{
    {\bf Spectroscopic youth diagnostics for Kepler-1627, KOI-7368,
    Kepler-1643, and KOI-7913 AB. }
    The spectra are shown in the observed frame, and the stars are
    sorted left-to-right in order of decreasing effective temperature.
    \label{fig:koiyouthindicators}
	}
\end{figure*}

Figure~\ref{fig:koiyouthindicators} shows key portions of the HIRES
and TRES spectra for the Kepler objects in Cep-Her.  Lithium
absorption is obvious at 6708\AA\ in all stars except KOI-7913 B,
where it is marginal.  H$\alpha$ is in emission for both components of
KOI-7913, and in absorption for the hotter stars.  In the following,
we compare these observations against stars in benchmark open
clusters.

\subsection{Lithium}

\begin{figure*}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6a.pdf}
			\includegraphics[width=0.49\textwidth]{f6b.pdf}
		}

>>>>

%% Reintroduced the \received and \accepted commands from AASTeX v5.2.
%% Add "Submitted to " argument.
\received{2022 May 2}
\revised{---}
\accepted{---}
%\submitjournal{AAS Journals}
\shorttitle{Trio of Mini-Neptunes in Cep-Her}

@@

% 208 words (250 max)
\begin{abstract}
  %The best way to measure a planet's age is to ignore the planet and
  %pay attention to the star.
  Stellar positions and velocities from Gaia are yielding a new view
  of open cluster dispersal.  
  Here we present an analysis of a group
  of stars spanning Cepheus ($l=100^\circ$) to Hercules ($l=40^\circ$),
  hereafter the Cep-Her complex.  The group includes four Kepler
  Objects of Interest:
  Kepler-1643 b ($R_{\rm p} = 2.32 \pm 0.14\,R_\oplus$, $P = 5.3\ {\rm days}$),
  KOI-7368 b ($R_{\rm p} = 2.22 \pm 0.12\,R_\oplus$, $P = 6.8\ {\rm days}$), 
  KOI-7913 Ab ($R_{\rm p} = 2.34 \pm 0.18\,R_\oplus$, $P = 24.2\ {\rm days}$), and
  Kepler-1627 Ab ($R_{\rm p} = 3.85 \pm 0.11\,R_\oplus$, $P = 7.2\ {\rm days}$).
  The latter Neptune-sized planet is in part of the Cep-Her complex
  called the $\delta$\ Lyr\ cluster \citep{bouma_kep1627_2022}.  Here
  we focus on the former three systems, which are in other regions of
  the association.  Based on kinematic evidence from Gaia, stellar
  rotation periods from TESS, and spectroscopy, these three objects
  are also $\approx$40 million years (Myr) old.  More specifically, we
  find that Kepler-1643 is $46^{+9}_{-7}$\,Myr old, based on its
  membership in a dense sub-cluster of the complex called RSG-5.
  KOI-7368 and KOI-7913 are $36^{+10}_{-8}$\,Myr old, and are in a
  diffuse region that we call CH-2.  Based on the transit shapes and
  high resolution imaging, all three objects are most likely planets,
  with false positive probabilities of $6\times10^{-9}$,
  $4\times10^{-3}$, and $1\times10^{-4}$ for Kepler-1643, KOI-7368,
  and KOI-7913 respectively.  These planets demonstrate
  that mini-Neptunes with sizes of $\approx$2 Earth radii exist at ages
  of 40 million years.
\end{abstract}

@@

Many of the salient properties of the Kepler objects of interest in Cep-Her can be
gleaned from Figure~\ref{fig:age}.  The stars span spectral types of
G8V (Kepler-1627) to K6V (KOI-7913 A).  The secondary in the KOI-7913
system has spectral type $\approx$K8V.  And since a star with
Solar mass and metallicity arrives at the zero-age main sequence at
$t\approx40$ Myr \citep{choi_mesa_2016}, these stars are all in the
late stages of their pre-main-sequence contraction.

@@

To verify these parameters and to analyze youth
proxies such as the Li 6708\,\AA\ doublet and H$\alpha$, we acquired
spectra.  We also acquired high resolution imaging for each system, to
constrain the existence of visual companions, including possible bound
binaries.  We give the system-by-system details in Sections~\ref{subsec:kep1643}
through~\ref{subsec:koi7913}, and summarize their implications for
the youth of the stars in Section~\ref{subsec:specyouth}.

\subsection{Kepler\,1643}
\label{subsec:kep1643}

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<$$1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$
respectively \citep{chubak_2012}.  To infer the equivalent width of
the \ion{Li}{1} 6708\,\AA\ doublet, we followed the procedure
described by \citet{bouma_2021_ngc2516}.  This yielded a strong
detection: ${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with values
consistent at $<$$1$-$\sigma$ between the two epochs.   The quoted
value does not correct for the \ion{Fe}{1} blend at 6707.44\,\AA.  Given the purported age and
effective temperature of the star, the lithium equivalent width is
somewhat low.  We discuss this in greater depth in
Section~\ref{subsec:specyouth}.

@@

\subsection{KOI-7913}
\label{subsec:koi7913}

@@

\paragraph{Spectra}
We acquired Keck/HIRES spectra for KOI-7913 A on the night of 2021 Nov
13, and KOI-7913 B on the night of 2021 Oct 26.  The
\texttt{SpecMatch-Emp} machinery yielded $T_{\rm eff,A} = 4324 \pm
70\,{\rm K}$, and $T_{\rm eff,B} = 4038 \pm 70\,{\rm K}$.  The
remaining parameters were in agreement with those from the cluster
isochrone.  For the primary, we also found $[{\rm Fe/H}]= -0.06 \pm
0.09$, $v\sin i = 13.3 \pm 1.0\,\mkms$, and ${\rm RV}_{\rm sys} =
-17.8 \pm 1.1\,\mkms$.  For the secondary, these same parameters were
$[{\rm Fe/H}]= -0.01 \pm 0.09$, $v\sin i = 10.7 \pm 1.0\,\mkms$, and
${\rm RV}_{\rm sys} = -18.8 \pm 1.1\,\mkms$.  Neither of the KOI-7913
components shows strong lithium absorption, but this is expected given
their $\approx$K6V and $\approx$K8V spectral types.  They do however
both show H$\alpha$ in emission.  Broadly speaking, both observations
are consistent with a $\approx$40 Myr age for KOI-7913 (see
Section~\ref{subsec:specyouth}).

@@

\subsection{Spectroscopic Youth Indicators}
\label{subsec:specyouth}

\begin{figure*}[t]
	\begin{center}
		\leavevmode
			\includegraphics[width=0.9\textwidth]{f5.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Spectroscopic youth diagnostics for Kepler-1627, KOI-7368,
    Kepler-1643, and KOI-7913 AB. }
    The spectra are shown in the observed frame, and the stars are
    sorted left-to-right in order of decreasing effective temperature.
    \label{fig:koiyouthindicators}
	}
\end{figure*}

Figure~\ref{fig:koiyouthindicators} shows key portions of the HIRES
and TRES spectra for the Kepler objects in Cep-Her.  Lithium
absorption is obvious at 6708\AA\ in all stars except KOI-7913 B.  
H$\alpha$ is in emission for both components of
KOI-7913, and in absorption for the hotter stars.  Here, we compare
these observations against benchmark open clusters in order to
assess their implications for the stellar ages.

\subsubsection{Lithium}

\begin{figure}[tp]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6a.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6b.pdf}
		}

		\vspace{-0.35cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f6c.pdf}
		}
	\end{center}
	\vspace{-0.6cm}
	\caption{
    {\bf Lithium 6708\AA\ and H$\alpha$ equivalent widths for the
    objects of interest compared to young open clusters and field
    stars. } Positive equivalent width means absorption; negative
    equivalent width means emission.  
    {\it Top \& middle}:
    The field stars are KOIs from
    \citet{berger_identifying_2018}.  The ``40-50 Myr'' reference
    stars ({\it left}) are from IC\,2602 \citep{randich_gaiaeso_2018} and
    Tuc-Hor \citep{kraus_stellar_2014}.  The ``112 Myr'' stars
    are from the Pleiades
    \citep{soderblom_evolution_1993,jones_evolution_1996,bouvier_pleiades_lirot_2018}.
    The statistical uncertainties on
    the equivalent widths are shown, or else are
    smaller than the markers.
    {\it Bottom}:
    The H$\alpha$ comparison is against Tuc-Hor
    \citep[$\approx$$40$\,Myr;][]{kraus_stellar_2014}
    \label{fig:lithium}
	}
\end{figure}

Figure~\ref{fig:lithium} compares the measured lithium equivalent
widths of the Kepler objects against a few reference populations.  We
selected reference studies from the literature only when upper limits were
explicitly reported.  KOI-7368 and KOI-7913~A have secure lithium
detections, while for KOI-7913~B the detection is marginal (${\rm EW}_{\rm
Li} = 42^{+12}_{-19}$\,m\AA).  For all three stars, as well as for
Kepler-1627~A, the observed lithium equivalent width is consistent
with the stellar effective temperatures and a $\approx40$\,Myr age.

Kepler-1643, in RSG-5, is conspicuously below the 40-50$\,$Myr
sequence in the left-panel of Figure~\ref{fig:lithium}, though
above the field stars (${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA).
The right panel shows the comparison against the Pleiades, where
Kepler-1643 is more consistent with the observed dispersion in
lithium.

One explanation for the lack of Li in Kepler-1643 could be that it is a field
interloper; another could be that RSG-5 is much older than 50\,Myr.  We do
not favor either explanation.  
RSG-5 cannot be much older than 50\,Myr
based on its proximity to the $\delta$~Lyr cluster and IC\,2602 in the
CAMD, and because it is below the Pleiades in the 
rotation versus color diagram (Figure~\ref{fig:age}).
Kepler-1643 also seems highly unlikely to be a field interloper, 
because we demonstrated a $\approx$$1\%$ false positive probability
in our spatio-kinematic selection of RSG-5 members, and there is a 
similar independent chance
($\approx$$1\%$) of a field K2V star having a rotation period below the
Pleiades \citep{mcquillan_rotation_2014}.
This yields a puzzle: how could a star have spatial, kinematic, and rotational
evidence consistent with being in a $\approx$50\,Myr cluster,
but a low lithium content?

Our preferred explanation for Kepler-1643's meager lithium 
content is that the reference sample of IC\,2602 and Tuc-Hor
stars may not fully explore all possible stellar rotation
periods and lithium equivalent widths at this age. 
Considering the top panels of Figure~\ref{fig:lithium}, it is remarkable that in
50 million years, stars between $4500$\,K and $5200$\,K go from
having a tight lithium sequence to one with a dispersion
$\approx10\times$ greater.  The existence of the Li dispersion in
Pleiades-age K-dwarfs has been known for decades; it has also been
known that the stars with the largest lithium abundances are also the
most rapidly rotating
\citep{butler_pleiades_1987,soderblom_evolution_1993}.  More recent
analyses of this correlation have been reviewed by
\citet{bouvier_lithium-rotation_2020}.  The conclusion of that work
was that the origin of the rotation-lithium correlation likely lies
within pre-main-sequence stellar physics.  If so, one would expect the
IC\,2602 and Tuc-Hor K-dwarfs to show a larger intrinsic lithium
dispersion.  A recent analysis of the $\approx$40\,Myr
NGC~2547 by \citet{binks_2022} suggests that this may
be the case, though that study only had $\approx$10 stars in the relevant
effective temperature range.
This suggests that
RSG-5 and Cep-Her could be
worthy objects for a closer analysis of the lithium-rotation correlation
near the zero-age main sequence.

\subsubsection{H$\alpha$}

Balmer line emission, particularly in H$\alpha$, is expected for
low-mass stars of this age.  \citet{kraus_stellar_2014} for instance, in their
survey of Tuc-Hor ($\approx$40\,Myr), observed that all
cluster members with spectral types $>$${\rm K4.5V}$ had H$\alpha$ in
emission.  Ths is consistent with our observations: KOI-7913 shows
H$\alpha$ in emission for both components, and in absorption
for all of our other Kepler objects (Figure~\ref{fig:koiyouthindicators}, lower panel).  The double-peaked nature of the
emission, though not always present, is also common for
active stars.  Proxima Centauri, for instance, has double-peaked
H$\alpha$ emission \citep{collins_calculations_2017}.  Given
that we have ruled out spectroscopic binarity, the most
likely
explanation is self-absorption: photons near the center of the line
see a greater optical depth from higher layers of the chromosphere,
while photons on the wings are too far from the
rest-wavelength to excite electrons and be re-absorbed in the upper
layers.  The exact details of when a star's atmosphere reaches the
conditions for such self-absorption require non-local thermal
equilibrium models of the chromosphere
\citep{short_chromospheric_1998,2005A&A...439.1137F}.

@@

\begin{figure*}[!t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.93\textwidth]{f4.pdf}
	\end{center}
	\vspace{-0.6cm}
	\caption{
		{\bf Radii, orbital periods, and ages of transiting exoplanets}.
    Planets younger than a gigayear with ages more precise than a
    factor of three are emphasized. The Cep-Her planets are
    Kepler-1643~b ($\square$), KOI-7368~b ($\triangledown$),
    KOI-7913~Ab (X), and Kepler-1627~Ab (+).  Interesting trends in
    the population of planets younger than $10^8$ years old include {\it i)} their
    large sizes and {\it ii)} the lack of hot Jupiters.  The new
    objects of interest in Cep-Her have normal mini-Neptune sizes
    between 2 and 3\,$R_\oplus$, which is a novelty given their ages.
    Parameters are from the NASA Exoplanet Archive (2022 Apr 5).
		\label{fig:rp_period_age}
	}
\end{figure*}

@@

The most significant novelty about the planets in Kepler-1643,
KOI-7368, and KOI-7913 is that their sizes (2.2 to 2.3\,$R_\oplus$)
are normal relative to the known population of mini-Neptunes from
Kepler.  At field star ages, mini-Neptune sizes span 1.8\,$R_\oplus$
to 3.6\,$R_\oplus$, with the most common size being $\approx
2.4\,R_\oplus$
\citep{Fulton_et_al_2017}.  The known planets younger than
$10^8$ years are almost all larger, with sizes between 4 and
10$\,R_\oplus$
\citep{Mann_K2_33b_2016,David_et_al_2016,benatti_possibly_2019,david_four_2019,newton_tess_2019,rizzuto_tess_2020,bouma_cluster_2020,mann_toi1227_2022}.
Figure~\ref{fig:rp_period_age} explores this by showing
the sizes, orbital periods, and ages of the known transiting planets,
emphasizing planets with precise ages.  The smallest previously known
planets comparable to the new Cep-Her mini-Neptunes are AU~Mic~c
($3.0\pm0.2\,R_\oplus$, see \citealt{martioli_aumicbc_2021} and
\citealt{gilbert_flares_2022}), Kepler-1627~Ab ($3.8\pm0.2\,R_\oplus$;
\citealt{bouma_kep1627_2022}), and AU~Mic~d ($4.2\pm0.2\,R_\oplus$;
\citealt{plavchan_planet_2020}).

@@

RSG-5, and Kepler-1643's membership inside it, meet typical
expectations for a star claimed to be in an open cluster.  RSG-5 is an
obvious overdensity relative to the local field, and our membership
selection easily yielded a clean pre-main-sequence locus
(Figure~\ref{fig:age}).  CH-2, and KOI-7913 and KOI-7368's membership
inside it, do not meet these expectations in as obvious a manner.
This is because the CH-2 association is diffuse.

@@

Given its low density, in CH-2 truly a star cluster?  For this
discussion, we adopt the definition that a star cluster is a group of
at least 12 stars that was physically associated at its time of
formation.  The ``12'' is set to distinguish star clusters from
high-order multiples \citep[see][]{krumholz_star_2019}.  We explicitly
do not require a ``star cluster'' to be gravitationally bound:
dissolved clusters as well as their tidal tails are included in our
adopted definition of ``clusters''.  We similarly do not require a
threshold number of stars per unit spatial volume.  The latter point
acknowledges that an important factor in cluster identification is
also density in velocity space.  Perhaps once stellar rotation periods
and chemical abundances reach the same level of ubiquity as stellar
proper motions, they might enable further refinement of our ability to
discover stars that formed as part of the same event.

@@

It would be a worthy exercise to perform a similar
search for coeval phase-space neighbors on the entire dataset of known
exoplanet hosts.  For the time being, we can offer the anecdotal point
that in our experience, most stars do not have dozens of 40\,Myr
neighbors within a local volume of a few \!\kms\ and tens of parsecs.

@@

\paragraph{Cep-Her}
Our analysis to date has focused only on portions of Cep-Her that were
observed by Kepler: RSG-5, CH-2, and the $\delta$~Lyr cluster.  In
\citet{bouma_kep1627_2022} as well as this work, we have shown that
these groups share similar ages, and have kinematic correlations that
suggest a common origin.  With that said, the membership and
kinematics of the other Cep-Her groups shown in
Figure~\ref{fig:XYZvtang} deserve independent attention.  An important
aspect of the remaining work will be to acquire radial velocities of a
large subset of the stars, and to determine whether the traceback approach
could be applicable.  Wide-field spectroscopic surveys such as LAMOST
\citep{zhao_2012_LAMOST} or SDSS-V \citep{kollmeier_2017} could enable
such analyses, while also providing sensitivity to the Li 6708\,\AA\
line.  If Gaia DR3 provides RVS spectra for the brighter F and G
dwarfs, these would also contain the calcium infrared triplet as
another age indicator.  These indicators, combined with better
kinematics, would help in definitively unraveling the formation
history of the complex.

@@

Each system has multiple indicators of youth that support the reported
ages.  For Kepler-1643, the strongest youth indicator is its physical
and kinematic association with RSG-5.  Based on the color--absolute
magnitude diagram, we are able to select members of this cluster with
a false positive rate of a few percent (Figure~\ref{fig:age}).
Kepler-1643 is one such member.  While the stellar rotation period
period agrees with this assessment, the star's lithium equivalent
width is marginally low, which might motivate future exploration of
lithium depletion across FGKM stars in RSG-5 (see
Section~\ref{subsec:specyouth}).

@@

%\clearpage
\acknowledgements
%\raggedbottom
% Cycle 3 and 4
L.G.B{.} is supported by the Heising-Simons Foundation 51
Pegasi~b Fellowship and the NASA TESS GI Program (80NSSC21K0335
and 80NSSC22K0298).
R.K{.} is supported by the Heising-Simons Foundation.
J.L.C{.} is supported by NSF AST-2009840 and the NASA TESS GI Program
(80NSSC22K0299).
D.H. is supported by the Alfred P. Sloan Foundation and NASA (80NSSC19K0597).
%
% ACKNOWLEDGE PFS / CAMPANAS.
%
%This paper includes data collected by the TESS mission, which are
%publicly available from the Mikulski Archive for Space Telescopes
%(MAST).
%%
%Funding for the TESS mission is provided by NASA's Science Mission
%directorate.
%%
%We thank the TESS architects
%%(G.~Ricker, R.~Vanderspek, D.~Latham, S.~Seager, J.~Jenkins)
%and the many TESS team members for their
%efforts to make the mission a continued success.
%
%
%This study was based in part on observations at Cerro Tololo
%Inter-American Observatory at NSF's NOIRLab (NOIRLab Prop{.} ID
%2020A-0146; 2020B-0029 PI: Bouma), which is managed by the
%Association of Universities for Research in Astronomy (AURA) under a
%cooperative agreement with the National Science Foundation.
%
%
%Finally, this research has made use of the Keck Observatory Archive (KOA),
%which is operated by the W. M. Keck Observatory and the NASA Exoplanet
%Science Institute (NExScI), under contract with the National
%Aeronautics and Space Administration.
%We also thank the Keck Observatory staff for their support of
%HIRES and remote observing.  We recognize the importance that the
%summit of Maunakea has within the indigenous Hawaiian community, and
%are deeply grateful to have the opportunity to conduct observations
%from this mountain.
%
% The Digitized Sky Survey was produced at the Space Telescope Science
% Institute under U.S. Government grant NAG W-2166.
% Figure~\ref{fig:scene} is based on photographic data obtained using
% the Oschin Schmidt Telescope on Palomar Mountain.
%

@@
